Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-23 paper/paper.tex
pass on results

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & 18,943 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 37 & 37\\
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
\setlength{\tabcolsep}{2pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   14 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   16 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   17 & 8/08  & V8 & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   18 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & LO & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & HI & \jsc{} \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & HI & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & HI & \jerry{}   \\
    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & HI  & \jerry{}\\
    \midrule
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    \midrule
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & LO & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & HI & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & HI & \veight{}\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & HI & \jsc{}\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & HI & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & HI & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & HI & \jerry{}\\
    \midrule        
    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
    \midrule    
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 37 & 37\\
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
\setlength{\tabcolsep}{2pt}    
%  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test
    transplantation. Url columns anonymized.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
   14 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
   16 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
   17 & 8/08  & \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
   18 & 8/08  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
   19 & 8/16  & \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
   20 & 8/22  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
   21 & 8/22  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
   22 & 8/22  & \jsc{} & New &  & - & \smonkey{}\\
   \midrule
    \multirow{3}{*}{23}  & 
    \multirow{3}{*}{8/22} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
    &  &
    \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
    &  &
    \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
   \midrule
   24 & 8/23  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & LO & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & HI & \jsc{} \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & HI & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & HI & \jerry{}   \\
    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & HI  & \jerry{}\\
    \midrule
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    \midrule
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & LO & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & HI & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & HI & \veight{}\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & HI & \jsc{}\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & HI & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & HI & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & HI & \jerry{}\\
    \midrule        
    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
    \midrule
    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
    \multirow{2}{*}{radamsa} & \chakra{} & New &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
    & - & \multirow{2}{*}{HI} & \multirow{2}{*}{Test262}\\    
    & & &
    \veight{} & New &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
    & - &  & \\
    \midrule   
   \bottomrule
  \end{tabular}
\end{table*}
